Optimizing Structural Properties Of Neural Networks With Genetic Algorithms

### 2015-08-07 paper/paper.tex
small changes

\subsection{Topology Optimizations}
To find out whether the topology can be used to improve the learning, we
performed an optimization in which the networks were an interpolation
between sparse random connections (Erdös-Renyi) and a ring topology where
the $\RINGk$ nearest neighbors are connected (for non integer $\RINGk$, the
fractional part determines the probability to use $[\RINGk]$ or $[\RINGk]+1$).
Since we are interested in the influence of the topology, the parameters
gain and feedback are kept constant during the optimization process,
leaving the connection probability for ER topology $\ERprob$, the ring
connection length $\RINGk$ and the interpolation value $\ERtoRING$ between
ER and ring as free parameters.

>>>>

\subsection{Topology Optimizations}
To find out whether the topology can be used to improve the learning, we
performed an optimization in which the networks were an interpolation
between sparse random connections and a ring topology where
the $\RINGk$ nearest neighbors are connected (for non integer $\RINGk$, the
fractional part determines the probability to use $[\RINGk]$ or $[\RINGk]+1$).
Since we are interested in the influence of the topology, the parameters
$\gain$ and $\feedback$ are kept constant during the optimization process,
leaving the connection probability for ER topology $\ERprob$, the ring
connection length $\RINGk$ and the interpolation value $\ERtoRING$ between
ER and ring as free parameters.
